---
title: "power_2"
author: "Ryan Farhat-Sabet"
output: html_document
---

# Power Analysis 2

Design scenario: 3x3 factorial between-subjects design testing the impact of source cues (expert, influencer, control) and stimulus type (video, written, both) on the credibility of nutrition recommendations. It includes a pre-test and post-test that measures the credibility of recommendations before and after the treatment. Power is estimated from OLS on post-test with pre-test as a covariate, using cluster-robust standard errors by participant. Suggested effect sizes in parameters section below (see Section 4 for justification).  

```{r parameters, include =FALSE}
params <- list(
  # Effect sizes (on raw scale, SD = 1.5)
  expert_main = 0.35,           # Expert effect in written format
  influencer_main = 0.35,       # Influencer effect in written format
  expert_video_int = 0.15,      # Additional effect for expert on video
  expert_both_int = 0.15,       # Additional effect for expert with both
  influencer_video_int = 0.15,  # Additional effect for influencer on video
  influencer_both_int = 0.15,   # Additional effect for influencer with both

  # Pre-test coefficients
  pretest_coef = 0.55,          # Pre-test predicts post-test

  # Covariate effects (small)
  age_coef = 0.08,
  gender_coef = 0.10,
  trust_science_coef = 0.12,
  prior_belief_coef = 0.10,
  nutrition_literacy_coef = 0.08,
  trust_experts_coef = 0.15,
  trust_influencers_coef = 0.10,

  # Variance parameters
  outcome_sd = 1.5,             # Target SD for outcome
  icc = 0.5,                    # Intra-class correlation (pre-post)

  # Scale parameters
  intercept = 4.0,              # Baseline for control-written
  scale_min = 1,
  scale_max = 7,

  # Covariate distribution parameters
  age_mean = 35,
  age_sd = 12,
  trust_science_mean = 5,
  trust_science_sd = 1.2,
  prior_belief_mean = 4,
  prior_belief_sd = 1.3,
  nutrition_literacy_mean = 4,
  nutrition_literacy_sd = 1.2,
  trust_experts_mean = 5,
  trust_experts_sd = 1.3,
  trust_influencers_mean = 4,
  trust_influencers_sd = 1.4
)
```


```{r generate_covariates, include = FALSE, echo =FALSE}
generate_covariates <- function(n, params) {
  data.frame(
    participant_id = 1:n,
    age = pmin(80, pmax(18, rnorm(n, params$age_mean, params$age_sd))),
    gender = rbinom(n, 1, 0.5),
    trust_science = pmin(7, pmax(1, rnorm(n, params$trust_science_mean, params$trust_science_sd))),
    prior_belief = pmin(7, pmax(1, rnorm(n, params$prior_belief_mean, params$prior_belief_sd))),
    nutrition_literacy = pmin(7, pmax(1, rnorm(n, params$nutrition_literacy_mean, params$nutrition_literacy_sd))),
    trust_experts = pmin(7, pmax(1, rnorm(n, params$trust_experts_mean, params$trust_experts_sd))),
    trust_influencers = pmin(7, pmax(1, rnorm(n, params$trust_influencers_mean, params$trust_influencers_sd)))
  )
}
```

```{r assign_treatment, include = FALSE, echo =FALSE}
assign_conditions <- function(n) {
  # Create all 9 conditions (3 sources × 3 formats)
  conditions <- expand.grid(
    source = c("Control", "Expert", "Influencer"),
    format = c("Written", "Video", "Both")
  )

  # Randomly assign participants to conditions
  assignments <- conditions[sample(1:9, n, replace = TRUE), ]

  # Create dummy variables
  data.frame(
    participant_id = 1:n,
    source = assignments$source,
    format = assignments$format,
    Expert = as.integer(assignments$source == "Expert"),
    Influencer = as.integer(assignments$source == "Influencer"),
    Video = as.integer(assignments$format == "Video"),
    Both = as.integer(assignments$format == "Both")
  )
}
```

```{r pre-test_scores, include = FALSE, echo = FALSE}
generate_pretest <- function(covariates, params) {
  n <- nrow(covariates)

  # Pre-test is influenced by baseline characteristics but not treatment
  pretest_base <- params$intercept +
    0.3 * (covariates$trust_science - params$trust_science_mean) +
    0.2 * (covariates$prior_belief - params$prior_belief_mean) +
    0.15 * (covariates$nutrition_literacy - params$nutrition_literacy_mean)

  # Add random error (contributes to between-person variance)
  pretest_error <- rnorm(n, 0, 0.8)

  # Combine and bound
  pretest <- pretest_base + pretest_error
  pmin(params$scale_max, pmax(params$scale_min, pretest))
}
```

```{r post-test_scores, include = FALSE, echo = FALSE}
generate_posttest <- function(data, params) {
  n <- nrow(data)

  # Center age for easier interpretation
  age_centered <- (data$age - params$age_mean) / 10  # Per 10 years

  # Calculate systematic component
  systematic <- params$intercept +
    # Treatment main effects
    params$expert_main * data$Expert +
    params$influencer_main * data$Influencer +
    # Treatment × Format interactions
    params$expert_video_int * data$Expert * data$Video +
    params$expert_both_int * data$Expert * data$Both +
    params$influencer_video_int * data$Influencer * data$Video +
    params$influencer_both_int * data$Influencer * data$Both +
    # Pre-test effect (creates ICC)
    params$pretest_coef * (data$pretest - params$intercept) +
    # Covariate effects
    params$age_coef * age_centered +
    params$gender_coef * data$gender +
    params$trust_science_coef * (data$trust_science - params$trust_science_mean) +
    params$prior_belief_coef * (data$prior_belief - params$prior_belief_mean) +
    params$nutrition_literacy_coef * (data$nutrition_literacy - params$nutrition_literacy_mean) +
    params$trust_experts_coef * (data$trust_experts - params$trust_experts_mean) +
    params$trust_influencers_coef * (data$trust_influencers - params$trust_influencers_mean)

  # Calculate residual SD to achieve target ICC
  # Total variance = between + within
  # ICC = between / total
  # We want: pretest explains some variance, residual provides rest
  total_var <- params$outcome_sd^2
  within_var <- total_var * (1 - params$icc)
  residual_sd <- sqrt(within_var * 0.7)  # 0.7 factor accounts for covariate variance

  # Add residual error
  posttest <- systematic + rnorm(n, 0, residual_sd)

  # Bound to scale
  pmin(params$scale_max, pmax(params$scale_min, posttest))
}
```

```{r simulate_data, include = FALSE}
generate_data <- function(n, params) {
  # Generate participant characteristics
  covariates <- generate_covariates(n, params)
  treatments <- assign_conditions(n)

  # Merge
  data <- merge(covariates, treatments, by = "participant_id")

  # Generate outcomes
  data$pretest <- generate_pretest(covariates, params)
  data$posttest <- generate_posttest(data, params)

  # Convert to long format (pre and post in separate rows)
  data_long <- data %>%
    select(participant_id, Expert, Influencer, Video, Both,
           age, gender, trust_science, prior_belief, nutrition_literacy,
           trust_experts, trust_influencers, pretest, posttest) %>%
    pivot_longer(cols = c(pretest, posttest),
                 names_to = "time",
                 values_to = "credibility") %>%
    mutate(post = as.integer(time == "posttest"))

  return(data_long)
}
```


```{r regression, cache=TRUE, include = FALSE}
analyze_data <- function(data) {
  # Keep only post-test
  data_post <- data %>% dplyr::filter(time == "posttest")
  
  # Join pre-test
  data_post <- data_post %>%
    dplyr::left_join(
      data %>% dplyr::filter(time == "pretest") %>%
        dplyr::select(participant_id, pretest = credibility),
      by = "participant_id"
    )
  
  # Basic sanity checks
  if (nrow(data_post) < 30) {
    return(c(p_expert = NA_real_, p_influencer = NA_real_))
  }
  if (length(unique(data_post$Expert)) < 2 ||
      length(unique(data_post$Influencer)) < 2) {
    # no variation in treatment indicators
    return(c(p_expert = NA_real_, p_influencer = NA_real_))
  }
  
  # Fit OLS
  model <- tryCatch(
    lm(credibility ~ Expert + Influencer +
         Video + Both +
         Expert:Video + Expert:Both +
         Influencer:Video + Influencer:Both +
         pretest +
         age + gender + trust_science + prior_belief +
         nutrition_literacy + trust_experts + trust_influencers,
       data = data_post),
    error = function(e) NULL
  )
  
  if (is.null(model)) {
    return(c(p_expert = NA_real_, p_influencer = NA_real_))
  }
  
  # Cluster-robust SEs
  coef_test <- tryCatch({
    vcov_cluster <- sandwich::vcovCL(model, cluster = ~ participant_id, type = "HC1")
    lmtest::coeftest(model, vcov = vcov_cluster)
  }, error = function(e) NULL)
  
  if (is.null(coef_test)) {
    return(c(p_expert = NA_real_, p_influencer = NA_real_))
  }
  
  # Extract p-values, guard against missing rows
  p_expert <- if ("Expert" %in% rownames(coef_test)) coef_test["Expert", "Pr(>|t|)"] else NA_real_
  p_influencer <- if ("Influencer" %in% rownames(coef_test)) coef_test["Influencer", "Pr(>|t|)"] else NA_real_
  
  c(p_expert = p_expert, p_influencer = p_influencer)
}
```


```{r simulation, cache=TRUE, include = FALSE}
run_one_simulation <- function(n, params, alpha = 0.05) {
  data <- generate_data(n, params)
  
  p_values <- tryCatch(
    analyze_data(data),
    error = function(e) c(p_expert = NA_real_, p_influencer = NA_real_)
  )
  
  # If p is NA, treat as not significant (0)
  expert_sig <- if (is.finite(p_values["p_expert"])) as.numeric(p_values["p_expert"] < alpha) else 0
  influencer_sig <- if (is.finite(p_values["p_influencer"])) as.numeric(p_values["p_influencer"] < alpha) else 0
  
  c(expert_sig = expert_sig, influencer_sig = influencer_sig)
}

```


```{r power, cache=TRUE, include = FALSE}
calculate_power <- function(n, params, n_sims = 1000, alpha = 0.05) {
  # Run simulations
  expert_results <- numeric(n_sims)
  influencer_results <- numeric(n_sims)

  for (i in 1:n_sims) {
    sim_result <- run_one_simulation(n, params, alpha)
    expert_results[i] <- sim_result["expert_sig"]
    influencer_results[i] <- sim_result["influencer_sig"]
  }

  # Calculate power (proportion of significant results)
  power_expert <- mean(expert_results)
  power_influencer <- mean(influencer_results)

  data.frame(
    sample_size = n,
    power_expert = power_expert,
    power_influencer = power_influencer
  )
}
```


```{r power_simulation, cache=TRUE, include = FALSE}
power_analysis <- function(n_range, params, n_sims = 1000, alpha = 0.05) {
  # Progress indicator
  cat("Running power analysis...
")

  # Run power calculation for each sample size
  results_list <- lapply(n_range, function(n) {
    cat(sprintf("  N = %d... ", n))
    result <- calculate_power(n, params, n_sims, alpha)
    cat("Done.
")
    return(result)
  })

  # Combine results
  do.call(rbind, results_list)
}
```


``` {r plotting, echo=FALSE, include = FALSE}
plot_power_curves <- function(power_results) {
  # Reshape for plotting
  plot_data <- power_results %>%
    pivot_longer(cols = c(power_expert, power_influencer),
                 names_to = "effect",
                 values_to = "power") %>%
    mutate(effect = recode(effect,
                          power_expert = "Expert vs Control",
                          power_influencer = "Influencer vs Control"))

  # Create plot
  ggplot(plot_data, aes(x = sample_size, y = power, color = effect, linetype = effect)) +
    geom_line(size = 1.2) +
    geom_point(size = 2) +
    geom_hline(yintercept = 0.80, linetype = "dashed", color = "gray40", size = 0.8) +
    annotate("text", x = max(plot_data$sample_size) * 0.95, y = 0.82, 
             label = "80% Power", color = "gray40", hjust = 1) +
    scale_color_manual(values = c("Expert vs Control" = "#0072B2", 
                                   "Influencer vs Control" = "#D55E00")) +
    scale_linetype_manual(values = c("Expert vs Control" = "solid", 
                                      "Influencer vs Control" = "dashed")) +
    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1),
                      labels = scales::percent_format(accuracy = 1)) +
    labs(
      title = "Power Analysis: Scenario 2 (Mixed Stimulus Formats)",
      subtitle = "Effect size d = 0.35 (0.30-0.40 depending on format), 1000 simulations per sample size",
      x = "Total Sample Size (N participants)",
      y = "Statistical Power",
      color = "Treatment Effect",
      linetype = "Treatment Effect"
    ) +
    theme_minimal(base_size = 12) +
    theme(
      legend.position = "bottom",
      plot.title = element_text(face = "bold", size = 14),
      panel.grid.minor = element_blank()
    )
}
```




```{r, echo=FALSE, results="hide", include = FALSE}
# Quick test at N = 150 with fewer sims
test_result <- calculate_power(150, params, n_sims = 100, alpha = 0.05)
test_result

```



```{r analysis, warning=FALSE, message=FALSE, cache=TRUE, include = FALSE}
# Define sample size range (60 to 200 in steps of 10)
sample_sizes <- seq(50, 500, by = 50)

# Run power analysis
# NOTE: This will take 2-3 minutes with 1000 simulations
power_results <- power_analysis(
  n_range = sample_sizes,
  params = params,
  n_sims = 1000,
  alpha = 0.05
)

```
```{r, include = FALSE, echo =TRUE}
# Display results
print(power_results)

# Create and display plot
power_plot <- plot_power_curves(power_results)
print(power_plot)
power_2 <- power_results
```
```{r}
# Display results
print(power_results)

```

```{r, cache=TRUE, include = FALSE}
# Find sample size needed for 80% power
n_for_80_expert <- power_results %>%
  filter(power_expert >= 0.80) %>%
  slice(1) %>%
  pull(sample_size)

n_for_80_influencer <- power_results %>%
  filter(power_influencer >= 0.80) %>%
  slice(1) %>%
  pull(sample_size)


print("Sample size for 80%% power (Expert):")
print(n_for_80_expert)
print("Sample size for 80%% power (Influencer):")
print(n_for_80_influencer)
```