---
title: "Untitled"
author: "Shashi Shamarao"
date: "2026-02-16"
output:
  pdf_document: default
  html_document: default
  latex_engine: xelatex
---
<!-- knit options in power.Rmd not needed here -->
```{r setup, include=FALSE, eval=FALSE}
knitr::opts_chunk$set(echo = ,TRUE)
options(repos = c(CRAN = "https://cloud.r-project.org"))
```

# Power Analysis 3

We are designing a multi-factor design to assess the power using monte carlo simulation
Factors to consider are:
Source: Expert vs Influencer
Content: Message vs Video or Both


Cells:
  
- Expert-Message
- Expert-Video
- Expert-Both
- Influencer-Message
- Influencer-Video
- Influencer-Both

Now pick the cell means that encode the interaction we care about
Example "true" means:

- Expert-Message - 4.8
- Expert-Video - 5.0
- Expert-Both - 5.5 (Expert video and message does slightly better)
- Influencer-Message - 4.2 
- Influencer-Video - 4.6
- Influencer-Both - 4.9

```{r parameters-1, warning=FALSE, message=FALSE, include = FALSE}
params1 <- list(
  # Effect sizes (on raw scale, SD = 1.5)
  expert_main = 0.35,           # Expert effect in written format
  influencer_main = 0.35,       # Influencer effect in written format
  expert_video_int = 0.15,      # Additional effect for expert on video
  expert_both_int = 0.15,       # Additional effect for expert with both
  influencer_video_int = 0.15,  # Additional effect for influencer on video
  influencer_both_int = 0.15,   # Additional effect for influencer with both

  # Pre-test coefficients
  pretest_coef = 0.55,          # Pre-test predicts post-test

  # Covariate effects (small)
  age_coef = 0.08,
  gender_coef = 0.10,
  trust_science_coef = 0.12,
  prior_belief_coef = 0.10,
  nutrition_literacy_coef = 0.08,
  trust_experts_coef = 0.15,
  trust_influencers_coef = 0.10,

  # Variance parameters
  outcome_sd = 1.5,             # Target SD for outcome
  icc = 0.5,                    # Intra-class correlation (pre-post)

  # Scale parameters
  intercept = 4.0,              # Baseline for control-written
  scale_min = 1,
  scale_max = 7,

  # Covariate distribution parameters
  age_mean = 35,
  age_sd = 12,
  trust_science_mean = 5,
  trust_science_sd = 1.2,
  prior_belief_mean = 4,
  prior_belief_sd = 1.3,
  nutrition_literacy_mean = 4,
  nutrition_literacy_sd = 1.2,
  trust_experts_mean = 5,
  trust_experts_sd = 1.3,
  trust_influencers_mean = 4,
  trust_influencers_sd = 1.4
)
```

```{r generate-covariates, warning=FALSE, message=FALSE, echo=FALSE, include = FALSE}
generate_covariates <- function(n, params1) {
  data.frame(
    participant_id = 1:n,
    age = pmin(80, pmax(18, rnorm(n, params1$age_mean, params1$age_sd))),
    gender = rbinom(n, 1, 0.5),
    trust_science = pmin(7, pmax(1, rnorm(n, params1$trust_science_mean, params1$trust_science_sd))),
    prior_belief = pmin(7, pmax(1, rnorm(n, params1$prior_belief_mean, params1$prior_belief_sd))),
    nutrition_literacy = pmin(7, pmax(1, rnorm(n, params1$nutrition_literacy_mean, params1$nutrition_literacy_sd))),
    trust_experts = pmin(7, pmax(1, rnorm(n, params1$trust_experts_mean, params1$trust_experts_sd))),
    trust_influencers = pmin(7, pmax(1, rnorm(n, params1$trust_influencers_mean, params1$trust_influencers_sd)))
  )
}
```

```{r assign-treatment, warning=FALSE, message=FALSE, include = FALSE}
assign_conditions <- function(n) {
  # Create all 9 conditions (3 sources × 3 formats)
  conditions <- expand.grid(
    source = c("Control", "Expert", "Influencer"),
    format = c("Written", "Video", "Both")
  )

  # Randomly assign participants to conditions
  assignments <- conditions[sample(1:9, n, replace = TRUE), ]

  # Create dummy variables
  data.frame(
    participant_id = 1:n,
    source = assignments$source,
    format = assignments$format,
    Expert = as.integer(assignments$source == "Expert"),
    Influencer = as.integer(assignments$source == "Influencer"),
    Video = as.integer(assignments$format == "Video"),
    Both = as.integer(assignments$format == "Both")
  )
}
```

```{r pre-test-scores, warning=FALSE, message=FALSE, echo=FALSE, include = FALSE}
generate_pretest <- function(covariates, params1) {
  with(covariates, {
    # linear predictor for pretest, centered around intercept
    eta_pre <- params1$intercept +
      params1$age_coef              * scale(age,   scale = FALSE) +
      params1$gender_coef           * gender +
      params1$trust_science_coef    * scale(trust_science,      scale = FALSE) +
      params1$prior_belief_coef     * scale(prior_belief,       scale = FALSE) +
      params1$nutrition_literacy_coef * scale(nutrition_literacy, scale = FALSE) +
      params1$trust_experts_coef    * scale(trust_experts,      scale = FALSE) +
      params1$trust_influencers_coef* scale(trust_influencers,  scale = FALSE)

    # residual variance for pretest (same SD as outcome for simplicity)
    pre <- rnorm(length(eta_pre), mean = eta_pre, sd = params1$outcome_sd)

    # clamp to Likert range
    pmin(params1$scale_max, pmax(params1$scale_min, pre))
  })
}
```

```{r post-test-scores, warning=FALSE, message=FALSE, echo=FALSE, include = FALSE}
generate_posttest <- function(covariates, treatment, pretest, params1) {
n <- nrow(covariates)

  # random intercept per participant to induce ICC between pre and post
  # ICC = tau^2 / (tau^2 + sigma^2) -> solve for tau^2
  sigma2 <- params1$outcome_sd^2
  tau2   <- params1$icc * sigma2 / (1 - params1$icc)
  subj_re <- rnorm(n, mean = 0, sd = sqrt(tau2))

  # treatment effects (3x3: source x format)
  with(cbind(covariates, treatment), {
    # base = control-written
    trt_effect <-
      Expert     * params1$expert_main +
      Influencer * params1$influencer_main +
      Expert     * Video * params1$expert_video_int +
      Expert     * Both  * params1$expert_both_int +
      Influencer * Video * params1$influencer_video_int +
      Influencer * Both  * params1$influencer_both_int

    # pretest effect
    pre_effect <- params1$pretest_coef * pretest

    # covariate effects (applied to post)
    cov_effect <- params1$age_coef              * scale(age,   scale = FALSE) +
                  params1$gender_coef           * gender +
                  params1$trust_science_coef    * scale(trust_science,     scale = FALSE) +
                  params1$prior_belief_coef     * scale(prior_belief,      scale = FALSE) +
                  params1$nutrition_literacy_coef * scale(nutrition_literacy, scale = FALSE) +
                  params1$trust_experts_coef    * scale(trust_experts,     scale = FALSE) +
                  params1$trust_influencers_coef* scale(trust_influencers, scale = FALSE)

    eta_post <- params1$intercept + trt_effect + pre_effect + cov_effect + subj_re

    post <- rnorm(n, mean = eta_post, sd = params1$outcome_sd)

    pmin(params1$scale_max, pmax(params1$scale_min, post))
  })
}
```


```{r simulate-scores, warning=FALSE, message=FALSE, include = FALSE}
simulate_dataset <- function(n, params1) {
  # covariates and treatment assignment
  covariates <- generate_covariates(n, params1)
  treatment  <- assign_conditions(n)

  # merge
  dat_wide <- merge(covariates, treatment, by = "participant_id")

  # pre and post
  dat_wide$pre  <- generate_pretest(dat_wide, params1)
  dat_wide$post <- generate_posttest(dat_wide, treatment, dat_wide$pre, params1)

  # manual wide -> long to keep participant_id as grouping factor
  pre_long <- dat_wide
  pre_long$time    <- factor("pre",  levels = c("pre", "post"))
  pre_long$outcome <- pre_long$pre

  post_long <- dat_wide
  post_long$time    <- factor("post", levels = c("pre", "post"))
  post_long$outcome <- post_long$post

  long <- rbind(
    pre_long[,  c("participant_id","time","source","format",
                  "age","gender","trust_science","prior_belief",
                  "nutrition_literacy","trust_experts","trust_influencers",
                  "outcome")],
    post_long[, c("participant_id","time","source","format",
                  "age","gender","trust_science","prior_belief",
                  "nutrition_literacy","trust_experts","trust_influencers",
                  "outcome")]
  )

  long$source <- factor(long$source, levels = c("Control","Expert","Influencer"))
  long$format <- factor(long$format, levels = c("Written","Video","Both"))
  long$participant_id <- factor(long$participant_id)
  
  long
}
```

```{r analyze-dataset, warning=FALSE, message=FALSE, include = FALSE}
analyze_dataset <- function(dat_long) {
  # make sure factors are correctly specified
  dat_long$source <- factor(dat_long$source, levels = c("Control","Expert","Influencer"))
  dat_long$format <- factor(dat_long$format, levels = c("Written","Video","Both"))
  dat_long$time   <- factor(dat_long$time,   levels = c("pre","post"))

  # fit mixed model: between (source, format), within (time), random intercept per participant
  fit <- lmer(
    outcome ~ source * format * time +
      age + gender + trust_science + prior_belief +
      nutrition_literacy + trust_experts + trust_influencers +
      (1 | participant_id),
    data = dat_long,
    REML = FALSE
  )

  # test the 3-way interaction using type III F-test
  an <- anova(fit, type = 3)  # from lmerTest
  # inspect once interactively: print(rownames(an))

  term_name <- "source:format:time"
  rn  <- rownames(an)
  idx <- match(term_name, rn)

  if (is.na(idx)) {
    p_int <- NA_real_
    conv  <- FALSE
  } else {
    p_int <- an[idx, "Pr(>F)"]
    conv  <- !is.na(p_int)
  }

  list(p_int = p_int, converged = conv)
}
```

```{r estimate-power, warning=FALSE, message=FALSE, include = FALSE, cache=TRUE, results="hide"}
estimate_power <- function(n, params1, nsim = 1000, alpha = 0.05, verbose = FALSE) {
  pvals      <- numeric(nsim)
  converged  <- logical(nsim)

  for (i in 1:nsim) {
    dat_long        <- simulate_dataset(n, params1)
    res             <- analyze_dataset(dat_long)
    pvals[i]        <- res$p_int
    converged[i]    <- res$converged

    if (verbose && i %% 50 == 0) {
      cat("Sim", i, "of", nsim, "\n")
    }
  }

  # estimated power and some diagnostics
  list(
    n               = n,
    nsim            = nsim,
    power           = mean(pvals < alpha, na.rm = TRUE),
    convergence_rate= mean(converged),
    mean_p          = mean(pvals, na.rm = TRUE),
    pvals           = pvals
  )
}

# Example: 300 participants total, nsim = 500 for quick check
res_300 <- estimate_power(n = 300, params1 = params1, nsim = 500, alpha = 0.05, verbose = TRUE)
res_300$power
res_300$convergence_rate
```

```{r power-grid, include = FALSE, warning=FALSE, message=FALSE, cache=TRUE, echo =TRUE}
library(dplyr)

n_grid <- c(150, 200, 250, 300, 350)  # total participants
nsim   <- 500

power_grid <- lapply(n_grid, function(nn) {
  cat("N =", nn, "\n")
  out <- estimate_power(n = nn, params1 = params1, nsim = nsim, alpha = 0.05)
  data.frame(
    n       = nn,
    power   = out$power,
    conv_rt = out$convergence_rate
  )
}) %>% bind_rows()

```
```{r plot-results, warning=FALSE, message=FALSE, include = FALSE, echo = TRUE}
library(ggplot2)

power3 <- ggplot(power_grid, aes(x = n, y = power)) +
  geom_line() +
  geom_point() +
  scale_y_continuous(limits = c(0, 1)) +
  labs(
    x = "Total sample size (N)",
    y = "Estimated power",
    title = "Monte Carlo power vs. total N for 3x3 mixed design"
  ) +
  theme_minimal()
power_3 <- power_grid
```
```{r}
print(power_grid)
```

>>>>>>> 7b86b9a (restoring Zev's version and adding in design descriptions)
