---
title: "power_1"
output: html_document
---

# Power Analysis 1

Design Scenario: Expert vs. Influencer (2 treatment + 1 control) (written stimuli)

We select tau based on small standardized mean difference (d=0.2) as a detectable benchmark as used in Case et al, 2022 with a 7-point Likert outcomes.

-   tau_expert = .4
-   tau_influencer = .2

```{r make-data, include=FALSE}
set.seed(1234)
# From previous study:
# Estimated ATE - .3
# Subjects - 1500
# Treatment mean - 2
# Control mean - 2.3
# Standard deviation - 2
# Rejection criteria p<.05

# Create data table
d <- data.table(id = 1:500) 

d[ , ':='(
  y0 = rnorm(.N, mean=0, sd=2),
  # We select tau based on  small standardized mean difference (d=0.2) as a detectable benchmark as used in
  # Case et al, 2022 with a 7-point Likert outcomes
  # With SD = 2, tau = d * SD
  # Expert: d = 0.2, tau = 0.2 * 2 =  .4 
  tau_expert = .4,
  # Influencer: Smaller effect, d=0.1. tau = .1 * 2 =  2
  tau_influencer = .2 
)]

# run the experiment: assign
d[ , treat_condition := sample(c("control", "expert", "influencer"),
                               size=.N, replace = TRUE)]

# run the experiment: measure
d[treat_condition == 'control',     Y := y0]
d[treat_condition == 'expert',       Y := y0 + tau_expert]
d[treat_condition == 'influencer', Y := y0 + tau_influencer ]

head(d, 3)


```

```{r first group-by, include=FALSE}
d[ , .(group_mean = mean(Y)), keyby = .(treat_condition)]
```

The model takes the form:
$$
Y_{i} = \beta_{0} + \beta_{1} * Expert + \beta_{2} * Influencer + \epsilon_{i}
$$
```{r, include=FALSE}
d[ , expert := treat_condition == 'expert']
d[ , influencer := treat_condition == 'influencer']
```

```{r estimate d-in-d model, echo=FALSE}
# Power analysis using robust standard errors
mod_1 <- d[ , lm(Y ~ 1 + expert + influencer)]
robust_se_mod_1 <- coeftest(mod_1, vcovHC)
```

```{r simulate experiment many times, include=FALSE, echo=TRUE}
# function used to run experiment with different sample sizes, later replicated to produce results
set.seed(1234)
simulate_exp <- function(N=500, tau_expert=.4, tau_influencer=.2){
  d <- data.table(id = 1:N)
  # Generate data
  d[ , ':='(
  y0 = rnorm(.N, mean=0, sd=2),
  tau_expert = tau_expert,
  tau_influencer = tau_influencer)
  ]
  # run the experiment:
  # assigning groups almost evenly until N length reached 
  d[ , treat_condition := sample(rep(c("control", "expert", "influencer"),
                                     length.out=.N))]
  # create individual treatment indicators
  d[ , expert := treat_condition == 'expert']
  d[ , influencer := treat_condition == 'influencer']
  # run the experiment: measure
  d[treat_condition == 'control',     Y := y0]
  d[treat_condition == 'expert',       Y := y0 + tau_expert]
  d[treat_condition == 'influencer', Y := y0 + tau_influencer]
  
  model <- d[ , lm(Y ~ 1 + expert + influencer)]
  robust_se <- coeftest(model, vcovHC)
  # Extracting p value from matrix 
  p_exp <- robust_se["expertTRUE", 4]
  p_infl <- robust_se["influencerTRUE", 4]
  c(expert=p_exp , influencer=p_infl)
}
```

```{r p_value_sample_10pct, include=FALSE}
obs <- nrow(d)
p_value_10pct <- replicate(1000, simulate_exp(N=round(.10 * obs)))
expert_power <- mean(p_value_10pct["expert", ] < .05) 
influencer_power <- mean(p_value_10pct["influencer", ] < .05) 
print(paste0("Expert power:", expert_power*100, "% Influencer Power:",
             influencer_power*100, "%"))
```

```{r p_value_sample_50pct, include=FALSE, cache=TRUE}
p_value_50pct <- replicate(1000, simulate_exp(N=round(.50 * obs)))
expert_power_50pct <- mean(p_value_50pct["expert", ] < .05) 
influencer_power_50pct <- mean(p_value_50pct["influencer", ] < .05)

expert_power_50pct 
influencer_power_50pct
```

```{r p_value_sample_100pct, include=FALSE, cache=TRUE}
p_value_100pct <- replicate(1000, simulate_exp(N=round(1 * obs)))
expert_power_100pct <-# 46%
influencer_power_100pct <- mean(p_value_100pct["influencer", ] < .05)

expert_power_100pct 
influencer_power_100pct
```

```{r p_value_sample_130pct, include=FALSE, cache=TRUE}
p_value_130pct <- replicate(1000, simulate_exp(N=round(1.30 * obs)))
expert_power_130pct <- mean(p_value_130pct["expert", ] < .05) 
influencer_power_130pct <- mean(p_value_130pct["influencer", ] < .05) 

expert_power_130pct 
influencer_power_130pct
```

```{r p_value_sample_200pct, include=FALSE, cache=TRUE}
p_value_200pct <- replicate(1000, simulate_exp(N=round(2.00 * obs)))
expert_power_200pct <- mean(p_value_200pct["expert", ] < .05) 
influencer_power_200pct <- mean(p_value_200pct["influencer", ] < .05) 

expert_power_200pct 
influencer_power_200pct

```

```{r p_value_sample_300pct, include=FALSE, cache=TRUE}
p_value_300pct <- replicate(1000, simulate_exp(N=round(3.00 * obs)))
expert_power_300pct <- mean(p_value_300pct["expert", ] < .05) 
influencer_power_300pct <- mean(p_value_300pct["influencer", ] < .05) 

expert_power_300pct 
influencer_power_300pct

```

```{r p_value_sample_500pct, echo=FALSE, include=FALSE, cache=TRUE}
p_value_500pct <- replicate(1000, simulate_exp(N=round(5.00 * obs)))
expert_power_500pct <- mean(p_value_500pct["expert", ] < .05) 
influencer_power_500pct <- mean(p_value_500pct["influencer", ] < .05)
print(paste0("Expert power:", expert_power_500pct*100, "% Influencer Power:", influencer_power_500pct*100, "%"))
```
```{r, include = FALSE}
power_dt <- data.table(
  sample_pct = c(0.10, 0.50, 1.00, 1.30, 2.00, 3.00, 5.00),
  N = obs * c(0.10, 0.50, 1.00, 1.30, 2.00, 3.00, 5.00),
  expert_power = c(
    expert_power,
    expert_power_50pct,
    expert_power_100pct,
    expert_power_130pct,
    expert_power_200pct,
    expert_power_300pct,
    expert_power_500pct
  ),
  influencer_power = c(
    influencer_power,
    influencer_power_50pct,
    influencer_power_100pct,
    influencer_power_130pct,
    influencer_power_200pct,
    influencer_power_300pct,
    influencer_power_500pct
  )
)

power_long <- melt(
  power_dt,
  id.vars = c("sample_pct", "N"),
  measure.vars = c("expert_power", "influencer_power"),
  variable.name = "treatment",
  value.name = "power"
)

power_long[ , treatment := fifelse(
  treatment == "expert_power", "Expert", "Influencer"
)]
```
```{r, include = FALSE, echo = TRUE}
plot1 <- ggplot(power_long, aes(x = N, y = power, color = treatment)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  geom_hline(yintercept = 0.80, linetype = "dashed") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0, 1)) +
  labs(
    title = "Power by Sample Size",
    x = "Sample Size (N)",
    y = "Statistical Power",
    color = "Treatment"
  ) +
  theme_minimal()
power_1 <- power_dt

```
```{r}
print(power_1)
```

With 10% (`r obs * .10` obs) of recruitment size of the original data we have a power of `r expert_power * 100`%, and `r influencer_power * 100`% for expert and influencer group respectively. Given our largest simulation with (`r obs * 5` obs) we obtain a power of `r expert_power_500pct * 100`%, and `r influencer_power_500pct * 100`% for expert and influencer group respectively.
