---
title: "Untitled"
author: "Shashi Shamarao"
date: "2026-02-17"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
options(repos = c(CRAN = "https://cloud.r-project.org"))
knitr::opts_chunk$set(echo = TRUE)
install.packages("ez")
library(ez)
library(pwr)
library(pwrss)
library(data.table)
library(ggplot2)
library(knitr)
library(dplyr)
library(tidyr)
library(car)
library(lme4)
library(lmerTest)
```

## R Markdown
We are designing a multi-factor design to assess the power using monte carlo simulation
Factors to consider are:
Source: Expert vs Influencer
Content: Message vs Video or Both


Cells:
Expert-Message
Expert-Video
Expert-Both
Influencer-Message
Influencer-Video
Influencer-Both

Now pick the cell means that encode the interaction we care about
Example "true" means:
Expert-Message - 4.8
Expert-Video - 5.0
Expert-Both - 5.5 (Expert video and message does slightly better)
Influencer-Message - 4.2 
Influencer-Video - 4.6
Influencer-Both - 4.9

## Global variables with default values
```{r cars}
# Global True parameters of the world
mu_Text_Expert   <- 4.7      # true mean in control
mu_Video_Expert <- 4.9
mu_Both_Expert <- 5.35 # (using the effect_size for both text and video for expert and influencer at 0.35)
  
mu_Text_Influencer <- 4.4
mu_Video_Influencer <- 4.7
mu_Both_Influencer <- 5.0

sigma        <- 1      # common standard deviation
rho <- 0.5 # correlation among repeated measures (rough, simple)
alpha        <- 0.05   # significance level
```

## Simulare one dataset for a given n per cell
1. We will simulate outcomes for each of the 6 cells
2. Run Anova for 2X3
3. Return whether LanguageXGrammar interaction is significant( p< alpha)

## One Experiment
```{r simulate_one_experiment, echo=FALSE}
simulate_one_experiment <- function(n_per_group) {
  # between-subjects groups
  groups <- c('Expert', 'Influencer')
  
  # Subject IDs and group assignment 
  Subject <- factor(1:(2 * n_per_group))
  Group <- factor(rep(groups, each = n_per_group))
  
  # Factor levels
  content_levels <- c('Text', 'Video', 'Both')
  
  # Build long data: each subject * each content
  dat <- expand.grid(
    Subject = Subject,
    Content = content_levels
  )
  dat$Group <- Group[dat$Subject]
  
  # Assign true mean for each cell 
  dat$mu <- with(dat, 
                 ifelse(Group == "Expert" & Content == "Text", mu_Text_Expert,
                 ifelse(Group == "Expert" & Content == "Video", mu_Video_Expert,
                 ifelse(Group == "Expert" & Content == "Both", mu_Both_Expert,
                 ifelse(Group == "Influencer" & Content == "Text", mu_Text_Influencer,
                 ifelse(Group == "Influencer" & Content == "Video", mu_Video_Influencer,
                 mu_Both_Influencer ))))))
  
  # subject random effect to induce correlation among the 3 formats
  subject_effect <- rnorm(length(Subject), mean = 0, sd = sqrt(rho) * sigma)
  dat$subj_eff <- subject_effect[dat$Subject]
  
  # condition-specific residual noise
  dat$eps <- rnorm(nrow(dat), mean=0, sd=sqrt(1-rho) * sigma)
  
  # Generate outcome: Y ~ Normal(mu_cell, sigma)
  dat$Y <- dat$mu + dat$subj_eff + dat$eps
  
  # Linear mixed model: random intercept per subject
  fit <- lmer(Y ~ Group * Content + (1 | Subject), data = dat)

  # Get p-value for Group:Content interaction
  an  <- anova(fit, type = 3)  # from lmerTest
  p_int <- an["Group:Content", "Pr(>F)"]

  reject <- p_int < alpha
  return(reject)
}
```

```{r estimate_power}
estimate_power <- function(n_per_group,
                           sims_coarse = 300,
                           sims_fine = 1500,
                           threshold = 0.08,
                           target_power = 0.8) {
  
  #calculate coarse estimate
  p_coarse <- mean(replicate(sims_coarse, 
                             simulate_one_experiment(n_per_group)))
  
  if (abs(p_coarse - target_power) > threshold) {
    return(p_coarse)  # good enough if far away
  } else {
    # refine when close to target
    p_fine <- mean(replicate(sims_fine, simulate_one_experiment(n_per_group)))
    return(p_fine)
  }
}

# # example: power when we have 30 per group
set.seed(123)
estimate_power(30)
```

```{r power_changes}
set.seed(123)
n_grid <- c(50, 60, 80, 100, 200, 300, 500, 750, 1000)

power_grid <- sapply(n_grid, estimate_power)

power_result <- data.frame(
  n_subjects = n_grid, 
  total_N = n_grid * 2,
  estimated_power = power_grid
)

# find closest n for a target power
find_n_from_grid <- function(target_power) {
  idx <- which.min(abs(power_result$estimated_power - target_power))
  power_result[idx, ]
}

power_80 <- find_n_from_grid(0.80)
power_95 <- find_n_from_grid(0.95)

power_result
power_80
power_95

cat("Closest samples to meet power 80%: ", as.character(power_80$estimated_power), "\n")
cat("Closest samples to meet power 80%: ", as.character(power_95$estimated_power), "\n")
```

```{r power-analysis-80 echo=FALSE}
# Power analysis at 80%
# power_analysis_80 <- function(target_power = 0.8, 
#                         start = 100,
#                           max = 400, 
#                           step = 40)
#  {
#  n  <- start
#  pw <- estimate_power(n)
#  while (pw < target_power && n <= max) {
#    n  <- n + step
#    pw <- estimate_power(n)
#  }
#  list(n_per_group = n,
#       total_subjects = 2 * n,
#       estimated_power = pw)
#}

#set.seed(123)
#power_analysis_80(0.80)
```

```{r power-analysis-95 echo=FALSE}
# Power analysis at 95%
# power_analysis_95 <- function(target_power = 0.95, 
#                            start = 200, 
#                            max = 500, 
#                            step = 50)
#   {
#   n  <- start
#   pw <- estimate_power(n)
#   while (pw < target_power && n <= max) {
#     n  <- n + step
#     pw <- estimate_power(n)
#   }
#   list(n_per_group = n,
#        total_subjects = 2 * n,
#        estimated_power = pw)
# }
# 
# set.seed(123)
# power_analysis_95(0.95)

```


```{r plot-results, warning=FALSE, message=FALSE echo=FALSE}
total_subjects <- length(n_grid)
ggplot(power_result,
       aes(x = total_N, y = estimated_power)) +
  geom_line(color = "steelblue", linewidth = 1) +
  geom_point(color = "steelblue", size = 2) +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, by = 0.1)) +
  labs(
    title = "Estimated power vs total N (mixed 2x3 design)",
    x = "Total N (participants)",
    y = "Power"
  ) +
  theme_minimal()
```
