---
title: "Diagnostic Checks"
author: "Zev Rosen"
date: "2026-04-11"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r libraries}
library(tidyr)
library(dplyr)
library(lmtest)
library(sandwich)
library(stargazer)
library(knitr)
```

```{r load_data}
d = readRDS("clean_data_zr.rds")
```

```{r reshape_data}
d_tidy <- d %>%
  rename(
    oil_infl_authentic  = post_oil_authentic,
    oil_infl_believable = post_oil_believable,
    dmy1_slp_attention  = attention1,
    dmy2_wt_attention   = attention2,
    oil_infl_attention  = attention_oil_inf,
    oil_exp_attention   = attention_oil_exp,
    meat_infl_attention = attention_meat_infl,
    meat_exp_attention  = attention_meat_exp
  ) %>%
  pivot_longer(
    cols = c(
      meat_exp_accurate, meat_exp_authentic, meat_exp_believable, meat_infl_accurate,
      meat_exp_attention, meat_infl_authentic, meat_infl_believable, meat_exp_cred,
      meat_infl_cred, meat_infl_attention,
      oil_exp_accurate, oil_exp_authentic, oil_exp_believable, oil_exp_cred,
      oil_exp_attention, oil_infl_accurate, oil_infl_cred, oil_infl_authentic,
      oil_infl_believable, oil_infl_attention,
      dmy1_slp_accurate, dmy1_slp_authentic, dmy1_slp_believable, dmy1_slp_attention,
      dmy2_wt_accurate, dmy2_wt_authentic, dmy2_wt_believable, dmy2_wt_attention
    ),
    names_to  = "variable",
    values_to = "value"
  ) %>%
  mutate(
    question = case_when(
      grepl("^meat", variable) ~ "meat",
      grepl("^oil",  variable) ~ "oil",
      grepl("^dmy1", variable) ~ "dmy1",
      grepl("^dmy2", variable) ~ "dmy2"
    ),
    inf_expert = case_when(
      grepl("exp",  variable) ~ "expert",
      grepl("infl", variable) ~ "influencer"
    ),
    metric = case_when(
      grepl("accurate",  variable) ~ "accurate",
      grepl("authentic", variable) ~ "authentic",
      grepl("believable",variable) ~ "believable",
      grepl("cred",      variable) ~ "cred",
      grepl("attention", variable) ~ "attention"
    )
  ) %>%
  group_by(across(-c(variable, value))) %>%
  summarise(value = mean(value, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(names_from = metric, values_from = value) %>%
  mutate(
    inf_expert          = ifelse(is.na(inf_expert), "", inf_expert),
    question_inf_expert = trimws(paste0(question, inf_expert))
  ) %>%
  mutate(
    position = case_when(
      order_pattern == "tfft" & question == "meat" ~ 1,
      order_pattern == "tfft" & question == "dmy1" ~ 2,
      order_pattern == "tfft" & question == "dmy2" ~ 3,
      order_pattern == "tfft" & question == "oil"  ~ 4,
      order_pattern == "ftft" & question == "dmy1" ~ 1,
      order_pattern == "ftft" & question == "meat" ~ 2,
      order_pattern == "ftft" & question == "dmy2" ~ 3,
      order_pattern == "ftft" & question == "oil"  ~ 4
    )
  ) %>%
  select(ResponseId, condition_sequence, order_pattern, question, inf_expert,
         question_inf_expert, position, accurate, authentic, believable, cred,
         attention, everything()) %>%
  filter(!(condition_sequence == "influencer_meat_expert_oil" &
             question_inf_expert %in% c("meatexpert", "oilinfluencer"))) %>%
  filter(!(condition_sequence == "expert_meat_influencer_oil" &
             question_inf_expert %in% c("meatinfluencer", "oilexpert")))

d_complete         <- d_tidy %>% filter(complete == 1)
d_attention_passed <- d_complete %>% filter(SC0 == 0)
```

# Data Checks

```{r data_checks, results='asis'}
# Balance across question types
table(d_complete$question, useNA = "ifany") %>%
  as.data.frame() %>%
  setNames(c("Question", "N")) %>%
  kable(caption = "Row counts by question type", booktabs = TRUE)

# Balance across source types
table(d_complete$inf_expert, useNA = "ifany") %>%
  as.data.frame() %>%
  setNames(c("Source", "N")) %>%
  kable(caption = "Row counts by source type", booktabs = TRUE)

# Check for duplicate respondent-question combinations
dupes <- d_complete %>%
  count(ResponseId, question, inf_expert, question_inf_expert) %>%
  filter(n > 1)
cat("Duplicate respondent-question rows:", nrow(dupes), "\n\n")

# Outcome variable summary statistics via stargazer
d_complete %>%
  select(accurate, authentic, believable, cred) %>%
  as.data.frame() %>%
  stargazer(
    type         = "latex",
    header       = FALSE,
    title        = "Outcome Variable Summary Statistics",
    summary.stat = c("n", "mean", "sd", "min", "max"),
    covariate.labels = c("Accurate", "Authentic", "Believable", "Credibility Index")
  )
```

\newpage
# Diagnostic 1: Randomization Balance

Tests whether treatment assignment (`condition_sequence`) predicts credibility — it should not in a well-randomized experiment.

```{r randomization, results='asis'}
model_order_meat <- lm(meat_cred ~ condition_sequence, data = d_attention_passed)
model_order_oil  <- lm(oil_cred  ~ condition_sequence, data = d_attention_passed)

se_order_meat <- sqrt(diag(vcovHC(model_order_meat, type = "HC1")))
se_order_oil  <- sqrt(diag(vcovHC(model_order_oil,  type = "HC1")))

stargazer(
  model_order_meat, model_order_oil,
  se               = list(se_order_meat, se_order_oil),
  title            = "Randomization Balance (Condition Sequence)",
  dep.var.labels   = c("Meat Credibility", "Oil Credibility"),
  covariate.labels = c("Influencer Meat / Expert Oil"),
  add.lines        = list(c("Robust SE", "Yes", "Yes")),
  omit.stat        = c("f", "ser"),
  type             = "latex",
  header           = FALSE,
  column.sep.width = "4pt"
)
```

\newpage
# Diagnostic 2: Order / Position Effects

Tests whether question presentation order (`order_pattern`: `ftft` vs `tfft`) predicts credibility — it should not.

```{r position, results='asis'}
model_position_meat <- lm(meat_cred ~ order_pattern, data = d_attention_passed)
model_position_oil  <- lm(oil_cred  ~ order_pattern, data = d_attention_passed)

se_position_meat <- sqrt(diag(vcovHC(model_position_meat, type = "HC1")))
se_position_oil  <- sqrt(diag(vcovHC(model_position_oil,  type = "HC1")))

stargazer(
  model_position_meat, model_position_oil,
  se               = list(se_position_meat, se_position_oil),
  title            = "Order / Position Effects",
  dep.var.labels   = c("Meat Credibility", "Oil Credibility"),
  covariate.labels = c("Order Pattern: tfft (vs ftft)"),
  add.lines        = list(c("Robust SE", "Yes", "Yes")),
  omit.stat        = c("f", "ser"),
  type             = "latex",
  header           = FALSE,
  column.sep.width = "4pt"
)
```

\newpage
# Diagnostic 3: Attention Check Effects

Tests whether failing attention checks (`SC0`) is associated with different credibility scores. Run on all completers (`d_complete`) to preserve variation in `SC0`.

```{r attention, results='asis'}
model_attention_meat <- lm(meat_cred ~ SC0, data = d_complete)
model_attention_oil  <- lm(oil_cred  ~ SC0, data = d_complete)

se_attention_meat <- sqrt(diag(vcovHC(model_attention_meat, type = "HC1")))
se_attention_oil  <- sqrt(diag(vcovHC(model_attention_oil,  type = "HC1")))

stargazer(
  model_attention_meat, model_attention_oil,
  se               = list(se_attention_meat, se_attention_oil),
  title            = "Attention Check Effects",
  dep.var.labels   = c("Meat Credibility", "Oil Credibility"),
  covariate.labels = c("Failed Attention Checks (SC0)"),
  add.lines        = list(c("Robust SE", "Yes", "Yes")),
  omit.stat        = c("f", "ser"),
  type             = "latex",
  header           = FALSE,
  column.sep.width = "4pt"
)
```

\newpage
# Diagnostic 4: Survey Duration Effects

Tests whether time spent on the survey predicts credibility — a proxy for satisficing or rushing behavior.

```{r duration, results='asis'}
model_duration_meat <- lm(meat_cred ~ `Duration (in seconds)`, data = d_attention_passed)
model_duration_oil  <- lm(oil_cred  ~ `Duration (in seconds)`, data = d_attention_passed)

se_duration_meat <- sqrt(diag(vcovHC(model_duration_meat, type = "HC1")))
se_duration_oil  <- sqrt(diag(vcovHC(model_duration_oil,  type = "HC1")))

stargazer(
  model_duration_meat, model_duration_oil,
  se               = list(se_duration_meat, se_duration_oil),
  title            = "Survey Duration Effects",
  dep.var.labels   = c("Meat Credibility", "Oil Credibility"),
  covariate.labels = c("Duration (seconds)"),
  add.lines        = list(c("Robust SE", "Yes", "Yes")),
  omit.stat        = c("f", "ser"),
  type             = "latex",
  header           = FALSE,
  column.sep.width = "4pt"
)
```