---
output: pdf_document
title: Pilot Analysis
---

`{r setup, include=FALSE} library(readr) library(data.table) library(stargazer) library(sandwich) library(lmtest) library(knitr)`

# =========================

# LOAD DATA

# =========================

`{r} d_rds = readRDS(here("data","processed","clean_pilot_data_zr.rds")) d = d_rds[keep_flag == 1]`

# =========================

# DESCRIPTIVE STATISTICS

# =========================

\`\`\`{r} vars \<- c("expert_trust_index", "health_engagement_index",
"meat_exp_cred", "meat_infl_cred", "oil_exp_cred", "oil_infl_cred",
"oil_cred", "meat_cred")

stargazer( as.data.frame(d\[, ..vars\]), type = "text", header = FALSE,
title = "Descriptive Statistics for Pilot Variables", summary.stat =
c("mean","sd","min","max") )

lapply(d\[, ..vars\], function(x) sum(is.na(x)))


    # =========================
    # HISTOGRAMS
    # =========================

    ```{r}
    hist(d$expert_trust_index, main = "Trust in Experts", xlab = "Index")
    hist(d$meat_exp_cred, main = "Meat Expert Credibility", xlab = "Credibility")
    hist(d$meat_infl_cred, main = "Meat Influencer Credibility", xlab = "Credibility")
    hist(d$oil_exp_cred, main = "Oil Expert Credibility", xlab = "Credibility")
    hist(d$oil_infl_cred, main = "Oil Influencer Credibility", xlab = "Credibility")

# =========================

# PAIRED T-TESTS

# =========================

\`\`\`{r} t_meat \<- t.test(d$meat_exp_cred, d$meat_infl_cred, paired =
FALSE) print(t_meat)

t_oil \<- t.test(d$oil_exp_cred, d$oil_infl_cred, paired = FALSE)
print(t_oil)


    # =========================
    # REGRESSION ANALYSIS
    # =========================

    ```{r}
    model_oil_1 <- lm(oil_cred ~ post_oil_source, data = d)
    coeftest(model_oil_1, vcov = vcovHC(model_oil_1, type = "HC1"))

    model_oil_2 <- lm(oil_cred ~ post_oil_source + expert_trust_index + health_engagement_index, data = d)
    coeftest(model_oil_2, vcov = vcovHC(model_oil_2, type = "HC1"))

    model_oil_3 <- lm(oil_cred ~ post_oil_source + expert_trust_index + health_engagement_index + age + gender + education, data = d)
    coeftest(model_oil_3, vcov = vcovHC(model_oil_3, type = "HC1"))

    model_oil_4 <- lm(oil_cred ~ post_oil_source * expert_trust_index + health_engagement_index, data = d)
    coeftest(model_oil_4, vcov = vcovHC(model_oil_4, type = "HC1"))

    model_oil_5 <- lm(oil_cred ~ post_oil_source * (expert_trust_index + health_engagement_index), data = d)
    coeftest(model_oil_5, vcov = vcovHC(model_oil_5, type = "HC1"))

    model_meat_1 <- lm(meat_cred ~ post_meat_source, data = d)
    coeftest(model_meat_1, vcov = vcovHC(model_meat_1, type = "HC1"))

    model_meat_2 <- lm(meat_cred ~ post_meat_source + expert_trust_index + health_engagement_index, data = d)
    coeftest(model_meat_2, vcov = vcovHC(model_meat_2, type = "HC1"))

    model_meat_3 <- lm(meat_cred ~ post_meat_source + expert_trust_index + health_engagement_index + age + gender + education, data = d)
    coeftest(model_meat_3, vcov = vcovHC(model_meat_3, type = "HC1"))

    model_meat_4 <- lm(meat_cred ~ post_meat_source * expert_trust_index + health_engagement_index, data = d)
    coeftest(model_meat_4, vcov = vcovHC(model_meat_4, type = "HC1"))

    model_meat_5 <- lm(meat_cred ~ post_meat_source * (expert_trust_index + health_engagement_index), data = d)
    coeftest(model_meat_5, vcov = vcovHC(model_meat_5, type = "HC1"))

# =========================

# ATTRITION ANALYSIS

# =========================

\`\`\`{r} table(d$complete)
mean(d$complete == 1, na.rm = TRUE)

table(d$post_meat_source, d$complete)
prop.table(table(d$post_meat_source, d$complete), 1)

t.test(complete \~ post_meat_source, data = d) lm(complete \~
post_meat_source, data = d)

table(d$post_oil_source, d$complete)
prop.table(table(d$post_oil_source, d$complete), 1)

t.test(complete \~ post_oil_source, data = d) lm(complete \~
post_oil_source, data = d)

lm(complete \~ post_meat_source + age + gender + expert_trust_index,
data = d) lm(complete \~ post_oil_source + age + gender +
expert_trust_index, data = d)

table(d$keep_flag)
table(d$keep_flag, d$complete)
prop.table(table(d$keep_flag, d\$complete), 1) \`\`\`
